---
title: "EM 2019 Check"
categories: []
tags: []
subtitle: ''
summary: ''
author: 'Giuseppe Carteny'
always_allow_html: true
slug: em19-check
output: 
  html_document: 
    toc: true
date: "2022-11-25"
lastmod: '2022-11-25T16:52:08+01:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r admin, echo=FALSE, warning=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}

# ADMIN #===============================================================================================

want = c("tidyverse",  "gridExtra", "magrittr", "haven", "data.table", "labelled", "here", "kableExtra")

have = want %in% rownames(installed.packages())
if ( any(!have) ) { install.packages( want[!have] ) }
junk <- lapply(want, library, character.only = TRUE)
rm(have,want,junk)

options(scipen = 99)
rm(list = ls())


# Load Euromanifesto data # ============================================================================

euroman.fls <- 
  list.files(here('content', 'post', '2022-11-25-EM2019','data'), pattern = 'Euromanifesto.dta') %>% 
  paste0(here('content', 'post', '2022-11-25-EM2019','data'), '/', .)

euroman.dfs <- lapply(euroman.fls, read_dta)


```

<br/><br/>

# Party codes {.tabset}

Czech Republic, Finland, Romania, Slovakia, and Sweden party codes include inconsistencies 
to be corrected.  
France, Germany, and Greece include cases that we might change, but they do not present
any relevant inconsistency. 

<br/>


<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover(); 
});
</script>

## Czech Republic 

The Tradition, Responsibility, Prosperity 09 (TOP 09) EES code is set as missing (-777), but actually 
the 2019 EES voter study code for this party is 1203530. 

```{r Cze2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  mutate(
    countryname = case_when(
      countryname == 'Czech Republic'  ~ 'Czech Rep.',
      countryname == 'UK'              ~ 'United Kingdom',
      countryname == 'The Netherlands' ~ 'Netherlands',
      T                                ~ countryname
    )
  ) %>% 
  filter(countryname=='Czech Rep.') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble


df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c(rep('',7), 'this should be 1203530', ''),
      title = NULL, 
      position = 'right'
    )
  )

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(8, bold = T, color = "white", background = "#65788c")

```

<br/><br/>

## Finland 

The swedish people's party ees code is set as missing (-777), but actually the 2019 EES voter study code 
for this party is 1246901. 

```{r Fin2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  filter(countryname=='Finland') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble 

df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c(rep('',6), 'this should be 1246901'),
      title = NULL, 
      position = 'right'
    )
  )

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(7, bold = T, color = "white", background = "#65788c")

```


<br/><br/>

## Romania

The USR - PLUS alliance 2019 EES code (1642402) seems to be wrong. In the EES the code for this alliance 
is actually 1642001. 


```{r Rom2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  filter(countryname=='Romania') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble 

df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c('', 'this should be 1642001', rep('',4)),
      title = NULL, 
      position = 'right'
    )
  )


df %>% 
  kbl(escape = F) %>% 
  # kable_paper(full_width=F)
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(2, bold = T, color = "white", background = "#65788c")

```

<br/><br/>

## Slovakia 

The Ordinary people and independent personalities (*Obyčajní ľudia a nezávislé osobnosti*) party EES 
code is set as missing (-777), but actually the 2019 EES voter study code for this party is 1703620.

```{r Slok2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  filter(countryname=='Slovakia') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble 

df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c(rep('',6), 'this should be 1703620', ''),
      title = NULL, 
      position = 'right'
    )
  )

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(7, bold = T, color = "white", background = "#65788c")

```

<br/><br/>

## Sweden

The *Socialdemokraterna* 2019 EES code (1752321) seems to be wrong. In the EES the code for this party 
is actually 1752320. 


```{r Swe2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  filter(countryname=='Sweden') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble 

df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c(rep('',3), 'this should be 1752320', rep('',5)),
      title = NULL, 
      position = 'right'
    )
  )


df %>% 
  kbl(escape = F) %>% 
  # kable_paper(full_width=F)
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(4, bold = T, color = "white", background = "#65788c")

```

<br/><br/>

## France 

The *Renaissance* and *Envie d'Europe Ecologique et Sociale* coalitions do not have an EES code. 
However, in the 2019 EES voter study one party for each coalition is available, namely 
*La Republique en Marche* (1250438) for the former and the Socialist Party (1250320) for the latter 
coalition. We could impute the EES codes of these parties. 


```{r Fra2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  filter(countryname=='France') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble 

df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c(rep('',2), 'this might be 1250320', 'this might be 1250438', rep('',2)),
      title = NULL, 
      position = 'right'
    )
  )


df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(3:4, bold = T, color = "white", background = "#8ca89c")

```

<br/><br/>

## Germany

Differently from the past, CDU and CSU in 2019 are computed together, and the code is 41501. 
Yet, CDU and CSU party codes are respectively 41521 and 41522. According to me, it might be more linear 
coding the coalition 41523, or alternatively 41521 since the CDU-CSU vote choice in the 2019 EES
German voter study is 1276521.

```{r Ger2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  filter(countryname=='Germany') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble %>% 
  mutate(
    ees = case_when(
      as.numeric(ees) < 0 ~ NA_real_,
      T       ~ as.numeric(ees)
    )
  ) %>% 
  filter(!is.na(ees))

df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c(rep('',4), 'this might be 41523 or 41521', rep('',2)),
      title = NULL, 
      position = 'right'
    )
  )


df %>% 
  kbl(escape = F) %>% 
  # kable_paper(full_width=F)
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(5, bold = T, color = "white", background = "#8ca89c")

```

<br/><br/>

## Greece 

The coalition "Kínima Allagís" does not have a EES code. 
However, in the 2019 EES voter study one party for this coalition is available, namely the PASOK 
(1300314). We could impute the EES codes of these parties. 


```{r Gre2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  left_join(
    .,
    tibble(
      country     = .$country %>% val_labels %>% as.numeric,
      countryname = .$country %>% val_labels %>% attr(., 'names') %>% trimws
    ),
    by = c('country')
  ) %>% 
  filter(countryname=='Greece') %>% 
  distinct %>% 
  dplyr::select(partyname, emcs, ees) %>% 
  as_tibble 

df$ees <- 
  cell_spec(
    df$ees,
    popover = spec_popover(
      content = c(rep('',2), 'this might be 1300314', rep('',5)),
      title = NULL, 
      position = 'right'
    )
  )

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#65788c", background = "#d2d4d6") %>% 
  row_spec(3, bold = T, color = "white", background = "#8ca89c")

```

<br/><br/>


# EU Institutions competences {.tabset}


According to the EMCS, the level for the following items is only the second one (EU level), and indeed 
2019 EM data do include only the variables for this level. 
Nonetheless, despite a similar coding scheme with 2019, the 2014 Euromanifesto data *do include* the 
other two levels (1 and 3), as shown in the following tabs. 
Now the question is: Are we going to update the 2014 EM dataset? Or are we going to ignore this 
inconsistency?


<br/><br/>


## EP 


2014:
```{r EPcomp2014, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[3]] %>% 
  dplyr::select(ends_with(c('306a', '306b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

2019:
```{r EPcomp2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  dplyr::select(ends_with(c('306a', '306b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```


## EU Commission 


2014:
```{r EUCOMcomp2014, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[3]] %>% 
  dplyr::select(ends_with(c('308a', '308b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 
  
df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

2019:
```{r EUCOMcomp2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  dplyr::select(ends_with(c('308a', '308b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left')  %>%  
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

 
## European Council 

2014:
```{r COUNCcomp2014, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[3]] %>% 
  dplyr::select(ends_with(c('310a', '310b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

2019:
```{r COUNCcomp2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  dplyr::select(ends_with(c('310a', '310b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

 
## Voting procedures Council 

2014:
```{r COUNCVOTEcomp2014, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[3]] %>% 
  dplyr::select(ends_with(c('3101a', '3101b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

2019:
```{r COUNCVOTEcomp2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  dplyr::select(ends_with(c('3101a', '3101b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

 
## EU court of justice

2014:
```{r ECJcomp2014, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- euroman.dfs[[3]] %>% 
  dplyr::select(ends_with(c('312a', '312b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

2019:
```{r ECJcomp2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  dplyr::select(ends_with(c('312a', '312b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

 
## EU competences in general

2014:
```{r EUcomp2014, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[3]] %>% 
  dplyr::select(ends_with(c('314a', '314b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")
```

2019:
```{r EUcomp2019, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE, eval=TRUE}

df <- 
  euroman.dfs[[4]] %>% 
  dplyr::select(ends_with(c('314a', '314b'))) %>% 
  mutate(across(names(.), ~round(.,2))) %>% 
  as_tibble %>% 
  head 

df %>% 
  kbl(escape = F) %>% 
  kable_styling(full_width=F, position = 'left') %>% 
  row_spec(1:nrow(df), bold = F, color = "#525252")

```

 



# Minor issues {.tabset}

## Country labels


The labels for NL and UK differ from those on the EES. We might change them. 

- Euromanifesto: "Czech Republic", "The Netherlands", "UK";
- EES voter study: "Czech Rep.", "Netherlands", "United Kingdom".


<br/><br/>
<br/><br/>
<br/><br/>



